% LaTeX file for resume 
% This file uses the resume document class (res.cls)
\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font \setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\usepackage{multicol}
\usepackage[usenames, dvipsnames]{color}

\usepackage{times} 
\usepackage{framed}
\usepackage{minibox}
\usepackage[margin=.05in]{geometry}
%\usepackage[a4paper, total={7in, 10 in}]{geometry}


\begin{document} 
\newcommand{\myheading}[5]{ \vspace*{0 in}    \hspace{.08 pt}
\begin{minipage}{4.12 in}
{\Large \textbf{#1}}\vspace{.2 in}
\end{minipage}  
\begin{minipage}{3 in }
$\bullet$ \hspace{1pt} E-mail: #2\\ \hspace{25 pt}  $\bullet$ \hspace{1pt} Phone: #3
\end{minipage} 

\vspace{-.45 in}
}
\myheading{Peter Caya}{petercaya@gmail.com}{(585)-378-0661}



 
\begin{resume}
	
%	Commands defining lines, section headings.
\newcommand{\LINE}{\rule{.88\linewidth}{.75 pt}\\}
\newcommand{\Line}{\rule{.87\linewidth}{.5 pt}\\}
\newcommand{\secspace}{\vspace {.15 in}}
\newcommand{\subsecspace}{\vspace{.05 in}}


\newcommand{\relcourse}[4]{\begin{ncolumn}{2}   \vspace{-.1 pt} \textit{Rochester Institute of Technology, Rochester NY} & \vspace{-.1 pt} \underline{Relevant Coursework:}  \\
M.S. in Applied and Computational Mathematics &  #1  	\\
 \textbf{GPA: \hspace{3 pt}  3.22/4.0} & #2\\
  & #3   \\
  & #4   \\      \end{ncolumn}\vspace{-25 pt} }


\definecolor{mygrey}{gray}{.8}
\newcommand{\resheading}[1]{{\LINE \large \colorbox{mygrey}{\begin{minipage}{.87\linewidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}

\vspace{15 pt}

%\resheading{Objective:}\\\vspace{- 18 pt}
%To contribute to data based research on social networks by combining tools from computational math and statistical learning to clean    
\vspace{- 18 pt}

\resheading{Education:}\\
\relcourse{Financial Engineering}{Scientific Computing}{Numerical Linear Algebra}{Inverse Problems}

\begin{ncolumn}{2}
 \textit{St.Bonaventure University, St.Bonaventure, NY} \\
  B.B.A., Magna cum Laude in Finance, 2012  \\
   \textbf{GPA:\hspace{3 pt} 3.61/4.0} &   \\
   &     \\ 
  \end{ncolumn} \\ 
\resheading{Technical Skills}\\
\vspace{-5 pt}\\
\begin{minipage}{.5\textwidth} \normalsize{ \underline{ Technology:}    }
		
		\begin{minipage}{1.25\textwidth} 
			\begin{itemize}
			\item R - Data cleaning, database querying, and classification algorithms.
			\item Excel - Proficiency with array formulas, index, and offset functions.
			\item MATLAB - Numerical optimization and solvers for differential equations.
		\end{itemize}
		\end{minipage}
\end{minipage}
\begin{minipage}{1.25\textwidth} 
\normalsize{\underline{ Background:}}

		\begin{minipage}{.2\textwidth} 
			\begin{itemize}
			\item Data cleaning and validation.
			\item Hypothesis testing and econometrics.
			\item Visualization of data analysis.
		\end{itemize}
		\end{minipage}

\end{minipage} \\

\vspace{-20 pt}
\resheading{Experience:}\\

%1111111111111111111111
\newcommand{\jobdesc}[5]{
\begin{minipage}{\textwidth}	
	\begin{minipage}{.2\textwidth}
\vspace{#5 pt}
	\textit{#1}\\
	#2 \\
	#3
	\end{minipage}
	\begin{minipage}{.75\textwidth}
	#4
	\end{minipage}
\end{minipage}
}

\vspace{-10 pt}

\jobdesc{Junior Business Analyst}{Forensic Economics}{January 2016 - Present}{
\begin{itemize}
\item Initiate securities fraud investigations by collecting, cleaning, and validating financial data from\\ Bloomberg, Capital IQ, SEC EDGAR, and other sources.
\item Assist expert witnesses in econometric analysis by using R to fit and compare statistical models \\for stock return behavior.
\item Contribute to arguments in expert reports by summarizing statistical and econometric conclusions \\using data visualizations.
\end{itemize} }{-35}\\
%1111111111111111111111


\vspace{-5 pt}
\jobdesc{Teaching Assistant}{Rochester Institute of\\ Technology}{September 2013 - May 2015}{\begin{itemize}
\item Ensured student understanding of course material by assisting in instruction and consulting\\ with Professors regarding class progress.
\item Contributed to classroom experience by overseeing project and class work and offering\\ individual tutoring.
\end{itemize} 
}{-6}

%1111111111111111111111

\vspace{-10 pt}
\jobdesc{Graduate Researcher}{Rochester Institute of\\ Technology}{November 2013 - May 2014}{   \begin{itemize}
\item Evaluated effectiveness of kidney failure treatment by conducting hypothesis testing in R.
\item Aided in research presentation by conveying data requirements, and meaning of statistical\\ tests.
\end{itemize} 
}{11}

%1111111111111111111111


\vspace{0 pt}
\jobdesc{Options Operations Analyst}{Citigroup}{October  2012 - August 2013}{   \begin{itemize}
\item Guaranteed trade consistency by working in a team to investigate discrepancies in derivative\\ contracts.
\item Facilitated trade volume oversight using Access, Excel, and Outlook to furnish reports.
\item Expedited reporting tasks by designing spreadsheet tools with VBA to process transaction data.
\end{itemize}
}{-20}





\vspace{-20 pt}
\resheading{Projects and Presentations}\vspace{-25 pt}\\
     % suppress blank line after tabbing



\begin{tabbing}
   \hspace{2.3in}\= \hspace{1.6in}\= \kill % set up two tab positions
    An Introduction to R   \hspace{287 pt}\textit{St.Bonaventure University, 2016}  
   \end{tabbing}
  \vspace{-10 pt} 
 \begin{itemize}
\item Delivered presentation and led discussions on uses of R for research and in the classroom.
\item Discussed using exploratory data analysis, regression and plotting to generate demonstrations for class.
\end{itemize}






%
 \vspace{-15 pt}     % suppress blank line after tabbing
\begin{tabbing}
   \hspace{2.3in}\= \hspace{1.6in}\= \kill % set up two tab positions
    A Comparison of Optimization Methods for Elliptic Inverse Problems \hspace{90 pt} \textit{Joint Mathematical Meeting, 2015}  
   \end{tabbing}
  \vspace{-10 pt}     % suppress blank line after tabbing
\begin{itemize}
\item Conducted convergence and performance analysis of  optimization algorithms for parameter identification in second and fourth\\ order elliptic partial differential equations.
\end{itemize}
 \vspace{-15 pt}     % suppress blank line after tabbing
 \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.6in}\= \kill % set up two tab positions
   \end{tabbing}\vspace{-45 pt}  
    % suppress blank line after tabbing 
 \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.6in}\= \kill % set up two tab positions
 An Introduction to R Programming for Financial Analysis \hspace{138 pt} \textit{St.Bonaventure University, 2015}
   \end{tabbing}
  \vspace{-10 pt}     % suppress blank line after tabbing
\begin{itemize}
\item Demonstrated the use of statistical programming by writing scripts analyzing commodity price movements to evaluate market\\ entry opportunities.
\end{itemize}
 \vspace{-15 pt}     % suppress blank line after tabbing
 
 
 \begin{tabbing}
   \hspace{2.3in}\= \hspace{1.6in}\= \kill % set up two tab positions
    Excel Instructor  \hspace{308 pt}  \textit{Citigroup, 2013} 
   \end{tabbing}
  \vspace{-10 pt}     % suppress blank line after tabbing
\begin{itemize}
\item Presented tutorials on basic and intermediate Excel skills for securities processing analysts and management.
\item Acted as a resource for other employees in the time saving uses of Excel and VBA. 
\end{itemize}
\vspace{-15 pt}

\end{resume}
\end{document}






%\begin{tabbing}
%   \hspace{2.3in}\= \hspace{1.6in}\= \kill % set up two tab positions
%    An Introduction to R   \hspace{287 pt}\textit{St.Bonaventure University, 2016}  
%   \end{tabbing}
%  \vspace{-10 pt} 
% \begin{itemize}
%\item Delivered presentation and led discussions on uses of R programming for research and in the classroom environment.
%\item Demonstrated the basic plotting and data analysis functionality of R through example scripts.
%\end{itemize}





%   \begin{tabbing}
%   \hspace{2.3in}\= \hspace{3.3in}\= \kill % set up two tab positions
%    \textit{Teaching Assistant} \>Rochester Institute of Technology   \> September 2013 - May 2015
%   \end{tabbing}
%\vspace{-5 pt}
%\begin{itemize}
%\item Ensured student understanding of course material by assisting in instruction and consulting with Professors \\regarding class progress.
%\item Contributed to classroom experience by overseeing project and class work and offering individual tutoring.
%\end{itemize}   





%
%\vspace{-15 pt}   
%
%   \begin{tabbing}
%   
%   \hspace{2.6in}\= \hspace{3.3 in}\= \kill % set up two tab positions
%    
%    \textit{Graduate Researcher:} FAST K Study \hspace{10 pt} Rochester Institute of Technology \hspace{97 pt} November 2013 - May 2014
%                               \end{tabbing}	    % suppress blank line after tabbing
%\vspace{-5 pt}    
%    \begin{itemize}
%\item Evaluated effectiveness of kidney failure treatment using statistical tests in R.
%\item Worked closely with doctors to communicate data requirements and meaning of statistical tests.
%\end{itemize}

%\vspace{-.15in}	
%   \begin{tabbing}
%   \hspace{2.3in}\= \hspace{1.6in}\= \kill % set up two tab positions
%    \textit{ FX Options Operations Analyst} \>Citigroup, Getzville NY\> \hspace{43 mm }October  2012 - August 2013
%                        
%   \end{tabbing}
%   \vspace{-10 pt}     % suppress blank line after tabbing
%\begin{itemize}
%\item Guaranteed trade consistency by working in a team to investigate discrepancies in derivative contracts.
%\item Updates management weekly regarding trade flows, and ongoing issues in outstanding contracts.
%\item Facilitated trade volume oversight using Access, Excel, and Outlook to furnish reports.
%\item Expedited reporting tasks by designing spreadsheet tools with VBA to process transaction data.
%\end{itemize}
%
%\textit{Business Analyst Intern}  \hspace{66 pt}            Iroquois Group, Allegany NY			\hspace{115 pt}  				May 2011 - August 2011\vspace{-5 pt}\\
%
%\vspace{-10 pt}
%\begin{itemize}
%\item Eased payment reorganization by compiling information on regional accounts with Excel.
%\item Improved managerial oversight of branches by producing reports highlighting differences in regional sales. 
%\end{itemize}\vspace{-5 pt}
%\vspace{50 pt}
%\rule{16 cm}{.5 pt}\\

%\input{Projects.tex}


\jobdesc{An Introduction to R }{St.Bonaventure University}{August 20,2016}{   
 \begin{itemize}
\item Delivered presentation and led discussions on uses of R for research and in\\ the classroom.
\item Demonstrated the basic steps of exploratory data analysis, regression and plotting as well as how to generate examples and figures for class.
\end{itemize}
}{-32.5}

\vspace{10 pt}  
\jobdesc{An Introduction to R Programming for Financial Analysis}{St.Bonaventure University}{February 2015}
{\begin{itemize}
\item Demonstrated the use of R programs to conduct time-series and financial analysis to university investment fund.
\item Wrote scripts analyzing commodity price movements to evaluate market entry opportunities.
\end{itemize}}{-32.5}


\vspace{10 pt}  

\jobdesc{A Comparison of Optimization Methods for Elliptic Inverse Problems }{Joint Mathematical Meeting}{January 2015}{   
\begin{itemize}

\item Delivered research findings to audience of applied mathematicians.
\end{itemize}
}{-32.5}
\vspace{10 pt}  


\jobdesc{Excel Instructor }{Citigroup,2013}{}{   
\begin{itemize}
\item Prepared and presented tutorials for basic and intermediate Excel skills.
\item Acted as a resource for other employees in the time saving uses of Excel and VBA.
\end{itemize}
}{-32.5}


